---
title: "Assignment 1: Exploring XML data"
author: "Ayush Shah"
date: "8/21/2021"
output: 
  html_document:
    code_folding: hide
---
___

## Description

In this assignment, we  explore data from the website <https://www.federalregister.gov/> for the file <https://www.govinfo.gov/bulkdata/FR/2021/08/FR-2021-08-13.xml>


## Libraries and import data
##### (To view, select 'code' -->)

```{r 0, message=FALSE, echo=TRUE, results='hide'}
library(xml2)
library(tidyverse)
library(knitr)
library(ggplot2)

xml <- read_xml("https://www.govinfo.gov/bulkdata/FR/2021/08/FR-2021-08-13.xml")
```

## 1. Number of unique agencies in 'CNTNTS'

```{r 1}

length(unique(xml_find_all(xml, '/FEDREG/CNTNTS/AGCY/HD/text()')))

```

## 2. Categories of Announcements

```{r 2}
category = xml_text(xml_find_all(xml, "//CNTNTS/AGCY/CAT/HD"))
cat_df = as.data.frame(category)
cat_df = cat_df %>% group_by(category) %>% tally()

kable(cat_df, caption = "Number of Categories")
```
```{r fig.align='center'}

ggplot(cat_df, aes(x = category, y = n, color= category)) + 
  geom_bar(stat='identity', fill= "white")+
  ggtitle("Number of Categories of Announcements")

```

## 3. Agencies that made a notice in the category 'PROPOSED RULES'

```{r 3}

agencies = xml_find_all(xml, "//AGCY[CAT/HD/text() = 'PROPOSED RULES']/HD/text()")
xml_text(agencies)

```

## 4. SUBJECT of the second RULE

```{r 4}
subject <- xml_find_all(xml, '/FEDREG/RULES/RULE[2]/PREAMB/SUBJECT/text()')
xml_text(subject)

```

## 5. SUBJECT of NOTICES by 'Centers for Disease Control and Prevention'

```{r 5}
subjects = xml_find_all(xml, "//PREAMB[SUBAGY/text() = 'Centers for Disease Control and Prevention']/SUBJECT/text()")
xml_text(subjects)

```

## 6. Top AGENCY with more than 5 notices

```{r, 6}
notice = xml_text(xml_find_all(xml, "//NOTICES/NOTICE/PREAMB/AGENCY"))
notice_df = as.data.frame(notice) %>% group_by(notice) %>% tally()
notice_df = notice_df[notice_df$n > 5,]
kable(notice_df, caption = "Agencies with more than 5 notices")
```
```{r fig.align='center', fig.width=20, fig.height=14}
ggplot(notice_df, aes(x=notice, y=n, fill= notice))+
ggtitle("Agencies with >5 NOTICES")+
geom_bar(stat="identity", color="black")+
scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#468295", "#382093", "#129458"))+
  theme(text = element_text(size=20), axis.text.x = element_text(angle=15, hjust=1)) 

```