---
title: <font size = "20"><b>Assignment2 - Github APIs</b></font>
author: <font size = "10"><b>Ayush Shah</b></font>
date: <font size = "10">4/2/2021</font>
output: 
  html_document:
    code_folding: "show"
  
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


> ### In this assignment, we extract details of the user **gimite** from github and visualize a couple of interesting facts from the extracted data.

---

## **User Description:** 
### Hiroshi Ichikawa is software enthusiast from Japan with 211 [followers](https://github.com/gimite?tab=followers), 34 [repositories](https://github.com/gimite?tab=repositories) and goes by the user ID [gimite](https://github.com/gimite)
## **User URL:** 
### https://github.com/gimite

---

---
## Importing the required libraries

```{r}
library(gh)
library(tibble)
library(knitr)
library(dplyr)
library(tidyr)
library(foreach)
library(jsonlite)
library(purrr)
library(ggplot2)
```

## Acquiring token to get a higher API rate limit

```{r}
my_token = "543ae9ab6c41b34cc920b487f40f59c9b6fbbc5f"
Sys.setenv(GITHUB_TOKEN = my_token)

```
## Table 1 - User Information

> ### Contains the User Name, User Login, User ID, Public Repositories and the number of followers

```{r}

gimite <- gh("/users/gimite")

gimite_basic_details <- tibble(User_Name = gimite$name, User_Login = gimite$login, User_Id = gimite$id,  
                    Repositories = gimite$public_repos, Followers = gimite$followers)
kable(gimite_basic_details, caption = "__Basic User Details__", align = "l")

```
## Table 2 - User's followers' information

> ### Contains the User's followers' IDs, Names, their number of public repositories and the number of their followers

```{r}

#gimite_followers <- gh("/users/gimite/followers", .limit =Inf)

#names_of_followers <- map_chr(gimite_followers, function(x){x$login})

#ids_of_followers <- map_int(gimite_followers, function(x){x$id})

#followers_public_repos = map_int(names_of_followers, function(x){
 # individual = gh(paste("/users/", x, sep = ""))
  #return (individual$public_repos)
#})


#followers_followers = map_int(names_of_followers, function(x){
 # individual = gh(paste("/users/", x, sep = ""))
  #return (individual$followers)
#})


#gimite_follower_details = data.frame(
 # Follower_ID = ids_of_followers,
  #Follower_Name = names_of_followers,
  #Follower_Public_Repos = followers_public_repos,
  #Follower_Followers = followers_followers
#)

#kable(head(gimite_follower_details,5), caption = "__Follower Details__", align = "l")

```
## Table 3 - User's Repositories' details

> ### Consists of repository name, language used, size, forks count, stargazers count, watchers count and open issues count.  We also handle missing values in 'Language' column by assigning NA

```{r}
gimite_repos <- gh("/users/gimite/repos", .limit =Inf)

gimite_repos_names <- map_chr(gimite_repos, function(x){
  x$name
})

gimite_repos_language <- map(gimite_repos, function(x){
  val <- x$language; replace(val, is.null(val), NA)
  return (val)
})

gimite_repos_size <- map_chr(gimite_repos, function(x){
  x$size
})

gimite_forks_count <- map_chr(gimite_repos, function(x){
  x$forks_count
})

gimite_stargazers_count <- map_int(gimite_repos, function(x){
  x$stargazers_count
})

gimite_watchers_count <- map_chr(gimite_repos, function(x){
  x$watchers_count
})

gimite_open_issues <- map_chr(gimite_repos, function(x){
  x$open_issues_count
})

gimite_repos_language[sapply(gimite_repos_language, function(x) length(x)==0L)] <- NA

gimite_repos_language_value = unlist(gimite_repos_language)


gimite_repo_info = data.frame(
  "Name" = gimite_repos_names,
  "Language" = gimite_repos_language_value,
  "Size" = gimite_repos_size,
  "Forks_Count" = gimite_forks_count,
  "Stargazers_Count" = gimite_stargazers_count,
  "Watchers_Count" = gimite_watchers_count,
  "Open_Issues_Count" = gimite_open_issues
)
kable(head(gimite_repo_info,5), caption = "__Repository Details__", align = "l")
```
## Table 4 - Summary of Issues

> ### Consists of repository name, number of open issues in that repository, closed issues and average time taken to close an issue in that repository (in hours)

number of open issues for each repository:
```{r}
gimite_n_of_open_issues = map_int(gimite_repos_names, function(x){
  open_issues = gh(paste("/repos/gimite/", x, "/issues?state=open", sep = ""))
  return (nrow(map_df(open_issues, magrittr::extract, c("state"))))
})
```

number of closed issues for each repository:
```{r}
gimite_n_of_closed_issues = map_int(gimite_repos_names, function(x){
  closed_issues = gh(paste("/repos/gimite/", x, "/issues?state=closed", sep = ""))
  return (nrow(map_df(closed_issues, magrittr::extract, c("state"))))
})
```

List containing issues with created_at dates and closed_at dates of issues in all repositories:
```{r}
gimite_issues_list = map(gimite_repos_names, function(x){
  issues = gh(paste("/repos/gimite/", x, "/issues?state=closed", sep = ""))
  return (map_df(issues, magrittr::extract, c("id", "created_at", "closed_at","state"))
  )
})
```

List to get the average time taken to close issues in each repository:
```{r}
avg_time<- map(gimite_issues_list, function(x){
  summer = 0
  for (i in nrow(x)){
    per_issue = as.numeric(difftime(strptime(x$closed_at[i],"%Y-%m-%dT%H:%M:%SZ"),
                          strptime(x$created_at[i],"%Y-%m-%dT%H:%M:%SZ")),unit = "hours")
    summer = summer + as.numeric(per_issue)
  }
  return (round((summer/nrow(x)),5))
})
```

Converting list to numeric to handle empty cells:
```{r}
avg_numeric = as.numeric(avg_time)
```

Final table 4:
```{r}
gimite_issue_summary = tibble(
  "Repo_Name" = gimite_repos_names,
  "Open_Issues" = gimite_n_of_open_issues,
  "Closed_Issues" = gimite_n_of_closed_issues,
  "Avg_Hours_To_Close" = avg_numeric
)

gimite_issue_summary[is.na(gimite_issue_summary)] <- 0

kable(head(gimite_issue_summary,5), caption = "__Issues Summary__", align = "l")
```

__Displaying some other rows:__
```{r}
kable(gimite_issue_summary[19:23,], caption = "__Issues Summary__", align = "l")

```
## __VISUALIZATIONS:__

### __Part 1: Getting to know the language Hiroshi Ichikawa uses MOST for his projects __
### First is a bar graph
```{r}
ggplot(gimite_repo_info,  aes(x = factor(""), fill = Language) ) +
  geom_bar()+
  scale_fill_brewer(palette="Yellow")
```


## Below is the same plot but with polar system:
```{r}
ggplot(gimite_repo_info,
  aes(x = factor(""), fill = Language) ) +
scale_fill_brewer(palette="Yellow")+
  geom_bar() +
  coord_polar(theta = "y") +
  scale_x_discrete("")+
  theme_minimal()
```
## From the above 2 simple plots, we can decuce that Hiroshi Ichikawa's most repositories have been in the language - __Ruby__

---
--- 
## __Part 2: __ Closed issues VS Open Issues: Shows the average time to close an issue in the form of a plot

```{r}
gimite_issue_summary %>%
  ggplot(aes(x = Open_Issues,
             y = Closed_Issues, col = Open_Issues
            , size = avg_numeric)) +
  geom_point(alpha = 4) + stat_smooth(method = "lm")
```
